Improved state-space models for inference about spatial and temporal variation in abundance from count data

### 2012-09-14 Dail_Mad_ext.tex
added tables

\usepackage[a4paper,hmargin={2.4cm,2.4cm},vmargin={2.4cm,2.4cm}]{geometry}
\usepackage[mathlines,displaymath]{lineno}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[round,colon,authoryear]{natbib}
\usepackage{color, soul}
\usepackage{fancyvrb}
\usepackage{verbatim}
\usepackage[pdftex,colorlinks=true,citecolor=black,linkcolor=black,urlcolor=black,pdftex,pdfstartview=FitH,bookmarks=true]{hyperref}

@@

>>>>

\usepackage[a4paper,hmargin={2.4cm,2.4cm},vmargin={2.4cm,2.4cm}]{geometry}
\usepackage[mathlines,displaymath]{lineno}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[round,colon,authoryear]{natbib}
\usepackage{color, soul}
\usepackage{fancyvrb}
\usepackage{verbatim}
\usepackage[pdftex,colorlinks=true,citecolor=black,linkcolor=black,urlcolor=black,pdftex,pdfstartview=FitH,bookmarks=true]{hyperref}
\usepackage{rotating}

@@

% Tables

\begin{table}[t]
  \centering
  \caption{Changed parameter values, by series of simulations.  We
    simulated 1000 sets of data each combination of parameter values
    for 100 sites over 40 years.  We assumed that initial abundance
    ($\Lambda$) was Poisson distributed.  For the exponential growth
    simulations we included all combinations of low, medium, and high
    $\Lambda$, growth rate ($r$), and detection probability ($p$).  For the Ricker
    model simulations we used $\Lambda$ = 10 and $p$ = 0.25, and simulated low,
    medium, and high values of $r$ and equilibrium density ($K$).  For the
    Ricker + immigration dynamics model we fixed all parameters the
    same as the Ricker model (with $r$ = 0.05 and $K$ = 10) and simulated
    low, medium, and high values of immigration rate ($\iota$).}
  \begin{tabular}{lcccccccc}
    \hline
    & \multicolumn{3}{c}{Exponential Growth} && Ricker &&
    \multicolumn{2}{c}{Ricker + Immigration} \\
    \cline{2-4}     \cline{6-6}    \cline{8-9}
%    & \multicolumn{3}{c}{\rule{25mm}{.1pt}} & \rule{5cm}{.5pt} & \multicolumn{2}{c}{\rule{20mm}{.1pt}} \\
                & $\Lambda$ & $r$ & $p$ && $r$  && $K$ & $\iota$  \\
    \hline
    Low	        &1	&-0.01	&0.05	&&0.005	&&5	&0.005  \\
    Med	        &5	&0	&0.25	&&0.05	&&10	&0.05   \\
    High	&10	&0.005	&0.5	&&0.1	&&20	&0.5    \\
    \hline
  \end{tabular}
\end{table}

\vfill
%\clearpage
\newpage

% Perhaps stack the species

\begin{sidewaystable}
  \centering
  \small
  \caption{Model selection table for ovenbirds and golden-winged
    warblers in Maryland and Virginia, 1966-2010.  We present model name
    and number, number of parameters (Par.), and difference in Akaike's
    information criterion between each model and the top model of that
    set ($\Delta$AIC).  For each species, the first section compares
    models for initial abundance, the second for detection probability,
    and the third for dynamics.}
  \begin{tabular}[h]{lcclcc}
\hline
A. Ovenbirds	&&&		B. Golden-Winged Warblers \\
\hline
Model	&Par.	&$\Delta$AIC	&Model	&Par.	&$\Delta$AIC \\
A.1. NB[$\Lambda$(.)$\alpha$(.)]Growth[$r$(.)]$p$(.)	&4	&0
&B.1. ZIP[$\Lambda$(.)$\psi$(.)]Growth[$r$(.)]$p$(.)	&4	&0 \\
A.2. P[$\Lambda$(.)]Growth[$r$(.)]$p$(.)	&3	&1262.7
&B.2. NB[$\Lambda$(.)$\alpha$(.)]Growth[$r$(.)]$p$(.)	&4	&0.4 \\
A.3. ZIP[$\Lambda$(.)$\psi$(.)]Growth[$r$(.)]$p$(.)	&4
&1264.7	&B.3. P[$\Lambda$(.)]Growth[$r$(.)]$p$(.)	&3	&37.8 \\
A.4. NB[$\Lambda$(.)$\alpha$(.)]Growth[$r$(.)]$p$(wind+1st)	&8
&0	&B.4. ZIP[$\Lambda$(.)$\psi$(.)]Growth[$r$(.)]$p$(1st)	&5
&0 \\
A.5. NB[$\Lambda$(.)$\alpha$(.)]Growth[$r$(.)]$p$(wind)	&7	&0.9
&B.5. ZIP[$\Lambda$(.)$\psi$(.)]Growth[$r$(.)]$p$(.)	&4	&3.5 \\
A.6. NB[$\Lambda$(.)$\alpha$(.)]Growth[$r$(.)]$p$(1st)	&5	&5.0
&B.6. ZIP[$\Lambda$(.)$\psi$(.)]Growth[$r$(.)]$p$(wind+1st)	&8
&5.9 \\
A.7. NB[$\Lambda$(.)$\alpha$(.)]Growth[$r$(.)]$p$(.)	&4	&6.4
&B.7. ZIP[$\Lambda$(.)$\psi$(.)]Growth[$r$(.)]$p$(wind)	&7	&9.3 \\
A.8. NB[$\Lambda$(.)$\alpha$(.)]Ricker+Imm.[$r$(.)$K$(.)$\iota$(.)]$p$(wind+1st)
&10	&0	&B.8. ZIP[$\Lambda$(.)$\psi$(.)]Growth[$r$(.)]$p$(1st)
&5	&0 \\
A.9. NB[$\Lambda$(.)$\alpha$(.)]Gompertz+Imm.[$r$(.)$K$(.)$\iota$(.)]$p$(wind+1st)
&10	&8.4
&B.9. ZIP[$\Lambda$(.)$\psi$(.)]AR[$\gamma$(.)$\omega$(.)]$p$(1st)
&6	&1.7 \\
A.10. NB[$\Lambda$(.)$\alpha$(.)]Growth+Imm.[$r$(.)$\iota$(.)]$p$(wind+1st)
&9	&36.5
&B.10. ZIP[$\Lambda$(.)$\psi$(.)]Growth+Imm.[$r$(.)$\iota$(.)]$p$(1st)
&6	&2.0 \\
A.11. NB[$\Lambda$(.)$\alpha$(.)]AR+Imm.[$\gamma$(.)$\omega$(.)$\iota$(.)]$p$(wind+1st)
&10	&38.6
&B.11. ZIP[$\Lambda$(.)$\psi$(.)]Gompertz+Imm.[$r$(.)$K$(.)$\iota$(.)]$p$(1st)
&7	&2.6 \\
A.12. NB[$\Lambda$(.)$\alpha$(.)]Gompertz[$r$(.)$K$(.)]$p$(wind+1st)
&9	&190.9
&B.12. ZIP[$\Lambda$(.)$\psi$(.)]Gompertz[$r$(.)$K$(.)]$p$(1st)	&6
&3.0 \\
A.13. NB[$\Lambda$(.)$\alpha$(.)]Ricker[$r$(.)$K$(.)]$p$(wind+1st)
&9	&195.1
&B.13. ZIP[$\Lambda$(.)$\psi$(.)]AR+Imm.[$\gamma$(.)$\omega$(.)$\iota$(.)]$p$(1st)
&7	&3.7 \\
A.14. NB[$\Lambda$(.)$\alpha$(.)]Growth[$r$(.)]$p$(wind+1st)	&8
&271.3
&B.14. ZIP[$\Lambda$(.)$\psi$(.)]Ricker+Imm.[$r$(.)$K$(.)$\iota$(.)]$p$(1st)
&7	&4.2 \\
A.15. NB[$\Lambda$(.)$\alpha$(.)]AR[$\gamma$(.)$\omega$(.)]$p$(wind+1st)
&9	&273.7
&B.15. ZIP[$\Lambda$(.)$\psi$(.)]Ricker[$r$(.)$K$(.)]$p$(1st)	&7
&5.2 \\
A.16. NB[$\Lambda$(.)$\alpha$(.)]Constant[$\gamma$(.)$\omega$(.)]$p$(wind+1st)
&9	&1856.7
&B.16. ZIP[$\Lambda$(.)$\psi$(.)]Constant[$\gamma$(.)$\omega$(.)]$p$(1st)
&6	&12.5 \\
\hline
\end{tabular}
\end{sidewaystable}
